---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(shilohMATH4753)
```

# shilohMATH4753

This is a package which contains all the functions created over the course of the past semester's labs.
For all functions below, use ?functionname for more information -- this is just an overview.

## dotplotwithlm

This function creates a dot plot with the linear model drawn onto it.
Use it like: dotplotwithlm(data, x, y), where x and y are the relevant columns from data.

## fire

This is a dataset containing information on home damage caused by fires.

## mybin

This function simulates a binomial across many iterations. Use it like mybin(iter, n, p)
where iter is number of iterations, n is number of elements, and p is the proabability
of success.

## myboot2

This is a bootstrapping function which finds confidence intervals for population parameters given sample statistics. Use it like myboot2(iter, x, fun, alpha) where iter is number of iterations,
x is the sample data, fun is the function for the statistic, and alpha is the size of the tail.

## myci

This function generates a 95% confidence interval for the population mean. Use it like myci(x)
where x is the sample data.

## myclt

This function demonstrates the central limit theorem for the sum of a uniform distribution.
Use it like myclt(n, iter, a, b) where n is the sample size, iter is the number of
iterations, a is the lower limit of the distribution, and b is the upper limit.

## mymaxlik

This function finds the maximum likelihood estimate for a parameter. Use it like
mymaxlik(lfun, x, param) where x is the sample data, lfun is the function to apply
to all values, and param are the parameter values to consider.

## myncurve

This function creates a normal curve shaded from negative infinity to a. Use it like
myncurve(mu, sigma, a) where mu is the mean and sigma is the standard deviation of
the normal distribution.
